\begin{References}
[1] A. Krizhevsky, G. Hinton, et al., “Learning multiple layers of features
from tiny images,” 2009.
\
[2] J. Deng, W. Dong, R. Socher, L.-J. Li, K. Li, and L. Fei-Fei, “Imagenet:
A large-scale hierarchical image database,” in 2009 IEEE conference on
computer vision and pattern recognition, pp. 248–255, Ieee, 2009.
\
[3] Google, “Cartoon set.” https://google.github.io,
This data is licensed by Google LLC under a Creative Commons
Attribution 4.0 International License.

[1] J. Smith, J. Doe and F. Bar (2001) A ground-breaking study.
Journal of Amazing Research 5(11), pp. 29-34.

[2] J. Smith, J. Doe and F. Bar (2001) A ground-breaking study.
Journal of Amazing Research 5(11), pp. 29-34.

[3] J. Smith, J. Doe and F. Bar (2001) A ground-breaking study.
Journal of Amazing Research 5(11), pp. 29-34.

[4] IBM Cloud Education(2020), The official side of IBM
https://www.ibm.com/cloud/learn/convolutional-neural-networks

[5] Aqeel Anwar(2020), The official side of Towardsdatascience.
https://towardsdatascience.com/a-visualization-of-the-basic-elements-of-a-convolutional-neural-network-75fea30cd78d

[6] kaggle Age And Gender Dataset, official side of kaggle.
https://www.kaggle.com/datasets/nipunarora8/age-gender-and-ethnicity-face-data-csv?resource=download

[7] Wikipedia, wikipedia official website
https://en.wikipedia.org/wiki/Keras

[8] Tensorflow, tensorflow official website
https://www.tensorflow.org/

[9] Faroit, Faroit official website
https://faroit.com/keras-docs/0.2.0/optimizers/

[10] Great Laarning, Great Learning official website
www.mygreatlearning.com/blog/activation-functions/

[11] https://machinelearningmastery.com/boosting-and-adaboost-for-machine-learning/

[12] Hastie, T. and Tibshirani, R. and Friedman, J.(2009), The Elements of Statistical Learning.
[13] Regression analysis and resampling methods, (2019), Sexton, A. and Husom, E.
[14]Hands-On Machine Learning with Scikit-Learn and TensorFlow: Concepts, Tools, and Techniques to Build Intelligent Systems(2017), Aurélien Géronh.

\end{References}